---
title: "3Ddev"
# author: "Thomas Huet"
# date: "10/9/2021"
output: html_document
---

```{r setup, include=FALSE, echo=FALSE, results="asis", warning = F}
# knitr::opts_chunk$set(echo = TRUE)
# options(rgl.useNULL = TRUE) # Suppress the separate window
source("setup.R")
setupKnitr(autoprint = TRUE)
set.seed(123)
library(rgl)
library(MASS)
library(ks)
library(misc3d)
library(knitr)
library(kableExtra)
library(dplyr)
library(DT)
library(openxlsx)

# isotop dataset
path.data <- "C:/Rprojects/_coll/220808 CAA22/3dkernel/"
df.isotop <- read.xlsx(paste0(path.data, "3dkernel.xlsx"))
xyz.isotop <- c("var1", "var2", "var3")
color.isotop <- c("color")

# test
xyz.iris <- c("Sepal.Length", "Sepal.Width", "Petal.Length")
color.iris <- c("color")
n.sample.iris <- 20
iris.samp <- iris[sample(nrow(iris), n.sample.iris), c("Species", xyz.iris)]
```

Workflow:

* step 1: [Textured model](#text3d)

* step 2: [Sampling locations](#pts3d)

* step 3: [3D Kernel Density Estimation](#kde3d)

* step 4: [Fusion](#ana3d)

---

## Textured model {#text3d}
> Test model

Textured models coming from photogrammetry, lasergrammetry, etc. Displayed in the dans 3DHOP framework and hosted in GitHub: 

* [fibule](https://zoometh.github.io/3DHOP/minimal/fibule.html)

## Sampling locations {#pts3d}
> Observed dataset

3D values of the `df.isotop` dataframe (`r nrow(df.isotop)` individual). Colors are base on the `object` variable. Dataset:

```{r isotop-colors, echo = FALSE}
u.objects <- unique(df.isotop$object)
df.colors <- data.frame(object = u.objects,
                        color = rainbow(length(u.objects)),
                        stringsAsFactors = F
)
isotop.color <- merge(df.isotop, df.colors, by = "object")
datatable(
  isotop.color[, c(1:7)],
  rownames = FALSE,
  width = "50%",
  editable = FALSE) %>%
  formatStyle("object",
    backgroundColor = styleEqual(df.colors$object, 
                                 toupper(df.colors$color))
  )
```

## Interactive 3D visualisation {#kde3d}

RGL 3D window:

```{r rgl-test}
with(isotop.color, 
     plot3d(var1, var2, var3, 
            type="s",
            radius=.1,
            col = color))
```


## Kernel Density Estimation {#kde3d}

3D polygons for the isotopic values

```{r kde-obs, echo = T}
# options(rgl.useNULL = TRUE) # avoid the popup RGL device
x <- isotop.color[ , c(xyz.isotop, color.isotop)]
H.pi <- Hpi(x[ , xyz.isotop], pilot = "samse")
fhat <- kde(x[ , xyz.isotop], H = H.pi, compute.cont = TRUE)  
plot(fhat, drawpoints = TRUE)
```


## Fusion {#ana3d}

TODO: Fusion des donnees vectorielles points/ploygones 3D et du modele texture




